---
title: ''
author: ''
date: ''
output: 
  html_document:
    df_print: paged
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
    theme: "flatly"
    code_download: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}

  knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                        fig.width  = 6 * 1.67, fig.height = 6)

```

```{r}

  library(descr)
  library(tidyverse)
  library(viridis)
  library(testthat)
  library(knitr)
  library(plotly)
  library(gtsummary)
  library(patchwork)
  
```

```{r}

# Set colors/theme for plots

  col1 <- viridis(1, option = "A", end = 0.9, dir = -1)
  col2 <- viridis(1, option = "A")
# col3 <- viridis(1, option = "A", begin = 0.4)
  col3 <- "#21091F"
  col4 <- viridis(1, option = "A", begin = 0.6)
  col5 <- viridis(1, option = "A", begin = 0.1)

  my_theme <- theme_minimal() +
    theme(
      panel.background = element_rect(fill = col2), 
      axis.text = element_text(color = col1),
      axis.title = element_text(color = col1),
      plot.background = element_rect(fill = col2), 
      legend.background = element_rect(fill = col2), 
      legend.text = element_text(color = col4), 
      legend.title = element_text(color = col4), 
      axis.ticks = element_line(color = col1), 
      title = element_text(color = col1), 
      panel.grid = element_line(color = col3), 
      strip.text = element_text(color = col1), 
      plot.subtitle = element_text(color = col1),
      plot.caption = element_text(hjust = 0)
      )
  
  theme_set(my_theme)
  
```

```{r}

  load("data/data.RData") 

  expect_equal(nrow(data), length(unique(data$response_id)))
  
  start_n <- nrow(data)

```

```{r}

  finished_n <- table(data$finished)["TRUE"]
  finished_p <- round(finished_n / nrow(data) * 100, 1)

```

# Survey completion

There are `r start_n` total responses in the pharmacist survey dataset. Of these, `r finished_n` finished the survey (`r finished_p`%). 

Survey start dates ranged from `r min(as.Date(data$start_date))` to `r max(as.Date(data$start_date))`. 

**Figure: Survey accrual**

```{r}

  data |>
    arrange(start_date) |>
    group_by(finished) |>
    mutate(obs = 1, cum_obs = cumsum(obs)) |> 
    ungroup() |>
  ggplot(aes(x = start_date, y = cum_obs, color = finished)) +
    geom_step(size = 1) +
    scale_color_viridis(
      "Finished?", option = "A", begin = 0.6, discrete = TRUE
      ) +
    xlab("Date participants started the survey") +
    ylab("Cummulative number of participants") +
    theme(legend.position = "bottom") +
    labs(caption = paste0("n = ", nrow(data)))

```
<br>
<br>

Survey accrual was similar for those who did vs didn't finish the survey. 

**Figure: Survey progress for those that didn't finish the survey**

```{r}

  data |>
    filter(finished == "FALSE") |>
  ggplot(aes(x = progress)) +
    geom_histogram(fill = col4) +
    xlab("Survey progress (%)") +
    ylab("Number of participants") +
    labs(caption = paste0("n = ", nrow(data) - finished_n))

```
<br>
<br>

**Figure: Minutes spent on the survey for those that finished**

```{r}

  data |>
    filter(finished == "TRUE") |>
  ggplot(aes(x = duration_in_minutes)) +
    scale_x_log10() +
    geom_histogram(fill = col4) +
    xlab("Minutes spent on the survey") +
    ylab("Number of participants") +
    labs(caption = paste0("n = ", finished_n))

```
<br>
<br>

**Figure: Minutes spent on the survey for those that didn't finish**

```{r}

  data |>
    filter(finished == "FALSE") |>
  ggplot(aes(x = duration_in_minutes)) +
    scale_x_log10() +
    geom_histogram(fill = col4) +
    xlab("Minutes spent on the survey") +
    ylab("Number of participants") +
    labs(caption = paste0("n = ", nrow(data) - finished_n))

```
<br>
<br>

**Figure: Number of non-missing values across all survey variables for finishers**

```{r}

  data_frame(
    n_obs = unlist(map(
      data[data$finished == "TRUE",], function(x) table(is.na(x))["FALSE"]
      )),
    variable_name = names(data)
    ) |>
    mutate(variable_name = reorder(factor(variable_name), n_obs)) |>
    filter(n_obs != finished_n) |>
  ggplot(aes(x = variable_name, y = n_obs, fill = n_obs)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    labs(
      x = "Variable", y = "N non-missing values for variables with any missings"
      ) +
    scale_fill_viridis(guide = "none", option = "A", begin = 0.3) +
    theme(panel.grid = element_blank()) 

```
<br>
<br>

**Figure: Number of non-missing values across all survey variables for non-finishers**

```{r}

  data_frame(
    n_obs = unlist(map(
      data[data$finished == "FALSE",], function(x) table(is.na(x))["FALSE"]
      )),
    variable_name = names(data)
    ) |>
    mutate(variable_name = reorder(factor(variable_name), n_obs)) |> 
    filter(n_obs != nrow(data) - finished_n) |>
  ggplot(aes(x = variable_name, y = n_obs, fill = n_obs)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    labs(
      x = "Variable", y = "N non-missing values for variables with any missings"
      ) +
    scale_fill_viridis(guide = "none", option = "A", begin = 0.3) +
    theme(panel.grid = element_blank())

```
<br>
<br>

```{r}

  data |>
    select(finished, q1:q5, q7) |> 
  tbl_summary(
    by = finished,
    missing = "ifany", 
    missing_text = "Missing values",
    # type = list(
    #   everything() ~ "categorical"
    #   ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) |>
    modify_spanning_header(c(stat_1, stat_2) ~ "**Finished survey?**") |>
    add_overall() |>
    add_p(test = list(
      all_categorical() ~ "chisq.test"
      ))
```

```




```{r}

  data |>
    select(finished, starts_with("q2") & !contains("text")) |> 
    na.omit() |>
  tbl_summary(
    by = finished,
    missing = "ifany",
    missing_text = "Missing values",
    type = list(
      q2_1 ~ "categorical"
      ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) |>
    add_overall() |>
    modify_spanning_header(c(stat_1, stat_2) ~ "**Finished survey?**") |>
    add_p(test = list(
      all_categorical() ~ "chisq.test"
      ))
```
<br>
<br>

### Free text

```{r}

  data |> select(finished, q2_5_5_text) |> na.omit()

```
<br>
<br>

# Sources of information (Q3)

## Q3.1

**Table. `r attr(data$q3_1, "label")`**

```{r}

  data |>
    select(finished, starts_with("q3_1_") & !contains("text")) |> 
  tbl_summary(
    by = finished,
    missing = "ifany", 
    missing_text = "Missing values",
    # type = list(
    #   everything() ~ "categorical"
    #   ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) |>
    add_overall() |>
    modify_spanning_header(c(stat_1, stat_2) ~ "**Finished survey?**") |>
    add_p(test = list(
      all_categorical() ~ "chisq.test"
      ))
```
<br>
<br>

**Figure `r attr(data$q3_1, "label")`**

```{r}

  df <- data |>
    filter(!is.na(q3_1)) |>
    select(response_id, finished, starts_with("q3_t1_")) |> 
    group_by(finished) |>
    mutate(n_fin = n()) |>
    ungroup() |>
    pivot_longer(-c(response_id, finished, n_fin)) |>
    filter(value != "No") 

  df |>
    group_by(value, finished, n_fin) |>
    summarise(n = n()) |>
    mutate(prop = n / n_fin) |>
  ggplot(aes(x = value, fill = prop, y = prop)) +
    geom_bar(stat = "identity") +
    scale_fill_viridis(guide = "none", option = "A", begin = 0.4) +
    coord_flip() +
    xlab("") +
    ylab("Number of respondent's endorsing") +
    facet_wrap(~finished) +
    theme(panel.grid = element_blank()) +
    labs(caption= paste0("n = ", nrow(df), " total endorsements across ", length(unique(df$response_id)), " unique respondents"))
    
```
<br>
<br>

### Free text

```{r}

  data |> select(q3_1_9_text, finished) |> na.omit()

```
<br>
<br>

## Q3.2:5

**Table. Sources of information**

```{r}

  data |>
    select(finished, q3_2:q3_5, -q3_3_4_text) |> 
  tbl_summary(
    by = finished,
    missing = "ifany", 
    missing_text = "Missing values",
    # type = list(
    #   q2_1 ~ "categorical"
    #   ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) |>
    add_overall() |>
    modify_spanning_header(c(stat_1, stat_2) ~ "**Finished survey?**") |>
    add_p(test = list(
      all_categorical() ~ "chisq.test"
      ))
```
<br>
<br>

### Free text

```{r}

  data |> select(q3_3_4_text, finished) |> na.omit()

```
<br>
<br>

## Q3.7

**Figure: In what format would you prefer to receive correspondence about important medicine safety related information? (ranks)**

```{r}

  levs <- names(select(data, starts_with("q3_7")))
  labs <- unlist(map(data[levs], function(x) attr(x, "label")))

  data |>
    select(response_id, finished, starts_with("q3_7")) |> 
    pivot_longer(-c(finished, response_id)) |>
    mutate(name = factor(name, levels = levs, labels = labs)) |>
    mutate(value = as.numeric(value)) |>
    na.omit() |>
    group_by(name) |>
    mutate(total_ranks = 1 / sum(value)) |> 
    ungroup() |>
    mutate(name = reorder(factor(name), total_ranks)) |> 
  ggplot(aes(x = name, fill = factor(value))) +
    geom_bar(position = position_fill(reverse = TRUE)) +
    scale_fill_viridis(
      "Rank", option = "A", begin = 0.3, discrete = TRUE
      ) +
    guides(fill = guide_legend(nrow = 1)) +
    coord_flip() +
    theme(
      panel.grid = element_blank(), 
      legend.position = "bottom"
      ) +
    labs(x = "", y = "")
    
```
<br>
<br>

## Q3.6, 8, 9

**Table. Usefulness**

```{r}

  data |>
    select(finished, q3_6, q3_8, q3_9) |>
  tbl_summary(
    by = finished,
    missing = "ifany", 
    missing_text = "Missing values",
    # type = list(
    #   q2_1 ~ "categorical"
    #   ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) |>
    add_overall() |>
    modify_spanning_header(c(stat_1, stat_2) ~ "**Finished survey?**") |>
    add_p(test = list(
      all_categorical() ~ "chisq.test"
      ))
```
<br>
<br>

**Figure: Usefulness**

```{r}

  levs <- names(select(data, q3_6, q3_8, q3_9))
  labs <- unlist(map(data[levs], function(x) attr(x, "label")))

  data |>
    select(response_id, finished, q3_6, q3_8, q3_9) |>
    pivot_longer(-c(finished, response_id)) |>
    mutate(name = factor(name, levels = levs, labels = labs)) |>
    na.omit() |>
  ggplot(aes(x = name, fill = value)) +
    geom_bar(position = position_fill(reverse = TRUE)) +
    scale_fill_viridis(
      "Rank", option = "A", begin = 0.3, discrete = TRUE
      ) +
    guides(fill = guide_legend(nrow = 1)) +
    coord_flip() +
    scale_x_discrete(labels = function(x) str_wrap(x, 30)) +
    theme(
      panel.grid = element_blank(), 
      legend.position = "bottom"
      ) +
    labs(x = "", y = "")
```
<br>
<br>

# DHPCs (Q4)

## Q4.1

**Table: What is the main safety issue associated with Sodium Valproate which led to a DHPC letter in April 2018?** 

```{r}

  data |>
    select(finished, q4_1) |> 
  tbl_summary(
    by = "finished",
    missing = "ifany", 
    missing_text = "Missing values",
    # type = list(
    #   q2_1 ~ "categorical"
    #   ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    )  |>
    add_overall() |>
    modify_spanning_header(c(stat_1, stat_2) ~ "**Finished survey?**") |>
    add_p(test = list(
      all_categorical() ~ "chisq.test"
      ))

```
<br>
<br>

Query: check possible values here

## Q4.2

**Figure: What actions did you take following the most recent DHPC issued on April 2018 on sodium valproate? (finishers only)**

```{r}

  df <- data |>
    filter(!is.na(q4_2)) |>
    select(response_id, starts_with("q4_t2_")) |> 
    pivot_longer(-c(response_id)) |>
    filter(value != "No") |>
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) 

  df |>
  ggplot(aes(x = value, fill = n)) +
    geom_bar() +
    scale_fill_viridis(
      guide = "none", option = "A", begin = 0.4, discrete = FALSE
      ) +
    coord_flip() +
    xlab("") +
    ylab("Number of respondent's endorsing") +
    theme(panel.grid = element_blank()) +
    scale_x_discrete(labels = function(x) str_wrap(x, 30)) +
    labs(caption= paste0("n = ", nrow(df), " total endorsements across ", length(unique(df$response_id)), " unique respondents"))
    
```
<br>
<br>

**Table: What actions did you take following the most recent DHPC issued on April 2018 on sodium valproate?**

```{r}

  data |>
    select(finished, starts_with("q4_2_") & !contains("text")) |>
  tbl_summary(
    by = finished,
    missing = "ifany", 
    missing_text = "Missing values",
    # type = list(
    #   everything() ~ "categorical"
    #   ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    )  |>
    add_overall() |>
    modify_spanning_header(c(stat_1, stat_2) ~ "**Finished survey?**") |>
    add_p(test = list(
      all_categorical() ~ "chisq.test"
      ))
  
```
<br>
<br>

### Free text

```{r}

  data |> select(q4_2_6_text, finished) |> na.omit()

```
<br>
<br>

## Q4.3

**Table:What are the main safety issues associated with quinolone and fluoroquinolone antibiotics (e.g. ciprofloxacin, levofloxacin, moxifloxacin) which led to a recent DHPC?**

```{r}

  data |>
    select(finished, q4_3) |> 
  tbl_summary(
    by = "finished",
    missing = "ifany", 
    missing_text = "Missing values",
    # type = list(
    #   q2_1 ~ "categorical"
    #   ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    )  |>
    add_overall() |>
    modify_spanning_header(c(stat_1, stat_2) ~ "**Finished survey?**") |>
    add_p(test = list(
      all_categorical() ~ "chisq.test"
      ))
```
<br>
<br>

Query: check possible values here

## Q4.4

**Figure: What actions did you take following the most recent DHPC on quinolone and fluoroquinolone prescribing issued in June 2023? (finishers only)**

```{r}

  df <- data |>
    filter(!is.na(q4_4)) |>
    select(response_id, starts_with("q4_t4_")) |> 
    pivot_longer(-c(response_id)) |>
    filter(value != "No") |>
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) 

  df |>
  ggplot(aes(x = value, fill = n)) +
    geom_bar() +
    scale_fill_viridis(
      guide = "none", option = "A", begin = 0.4, discrete = FALSE
      ) +
    coord_flip() +
    xlab("") +
    ylab("Number of respondent's endorsing") +
    theme(panel.grid = element_blank()) +
    scale_x_discrete(labels = function(x) str_wrap(x, 30)) +
    labs(caption= paste0("n = ", nrow(df), " total endorsements across ", length(unique(df$response_id)), " unique respondents"))
    
```
<br>
<br>

**Table: What actions did you take following the most recent DHPC on quinolone and fluoroquinolone prescribing issued in June 2023?**

```{r}

  data |>
    select(finished, starts_with("q4_4_") & !contains("text")) |>
  tbl_summary(
    by = finished,
    missing = "ifany", 
    missing_text = "Missing values",
    # type = list(
    #   everything() ~ "categorical"
    #   ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    )  |>
    add_overall() |>
    modify_spanning_header(c(stat_1, stat_2) ~ "**Finished survey?**") |>
    add_p(test = list(
      all_categorical() ~ "chisq.test"
      ))
  
```
<br>
<br>

### Free text

```{r}

  data |> select(q4_4_10_text, finished) |> na.omit()

```
<br>
<br>

## Q4.5

Note: From this point forward, all of the non-finishers are missing data for the following responses. 

**Figure: Who opens the DHPC after it arrives in your email inbox/post in your pharmacy?**

```{r}

  df <- data |>
    filter(!is.na(q4_5)) |>
    select(response_id, starts_with("q4_t5_")) |> 
    pivot_longer(-c(response_id)) |>
    filter(value != "No") |>
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) 

  df |>
  ggplot(aes(x = value, fill = n)) +
    geom_bar() +
    scale_fill_viridis(
      guide = "none", option = "A", begin = 0.4, discrete = FALSE
      ) +
    coord_flip() +
    xlab("") +
    ylab("Number of respondent's endorsing") +
    theme(panel.grid = element_blank()) +
    scale_x_discrete(labels = function(x) str_wrap(x, 30)) +
    labs(caption= paste0("n = ", nrow(df), " total endorsements across ", length(unique(df$response_id)), " unique respondents"))
    
```
<br>
<br>

**Table: Who opens the DHPC after it arrives in your email inbox/post in your pharmacy?**

```{r}

  data |>
    filter(finished == "Yes") |>
    select(starts_with("q4_5_") & !contains("text")) |>
  tbl_summary(
    missing = "ifany", 
    missing_text = "Missing values",
    # type = list(
    #   everything() ~ "categorical"
    #   ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    )  

```
<br>
<br>

### Free text

```{r}

  data |> select(q4_5_6_text, finished) |> na.omit()

```
<br>
<br>

## Q4.6

**Figure: After the DHPC is opened, how is the communication implemented in the pharmacy?**

```{r}

  df <- data |>
    filter(!is.na(q4_6)) |>
    select(response_id, starts_with("q4_t6_")) |> 
    pivot_longer(-c(response_id)) |>
    filter(value != "No") |>
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) 

  df |>
  ggplot(aes(x = value, fill = n)) +
    geom_bar() +
    scale_fill_viridis(
      guide = "none", option = "A", begin = 0.4, discrete = FALSE
      ) +
    coord_flip() +
    xlab("") +
    ylab("Number of respondent's endorsing") +
    theme(panel.grid = element_blank()) +
    scale_x_discrete(labels = function(x) str_wrap(x, 30)) +
    labs(caption= paste0("n = ", nrow(df), " total endorsements across ", length(unique(df$response_id)), " unique respondents"))
    
```
<br>
<br>

**Table: After the DHPC is opened, how is the communication implemented in the pharmacy?**

```{r}

  data |>
    filter(finished == "Yes") |>
    select(starts_with("q4_6_") & !contains("text")) |>
  tbl_summary(
    missing = "ifany", 
    missing_text = "Missing values",
    # type = list(
    #   everything() ~ "categorical"
    #   ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    )  

```
<br>
<br>

### Free text

```{r}

  data |> select(q4_6_11_text, finished) |> na.omit()

```
<br>
<br>

## Q4.7

**Figure: How is the DHPC (i.e. Dear Pharmacist letter) disseminated to pharmacists and technicians in your pharmacy?**

```{r}

  df <- data |>
    filter(!is.na(q4_7)) |>
    select(response_id, starts_with("q4_t7_")) |> 
    pivot_longer(-c(response_id)) |>
    filter(value != "No") |>
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n))
    

  df |>
  ggplot(aes(x = value, fill = n)) +
    geom_bar() +
    scale_fill_viridis(
      guide = "none", option = "A", begin = 0.4, discrete = FALSE
      ) +
    coord_flip() +
    xlab("") +
    ylab("Number of respondent's endorsing") +
    theme(panel.grid = element_blank()) +
    scale_x_discrete(labels = function(x) str_wrap(x, 30)) +
    labs(caption= paste0("n = ", nrow(df), " total endorsements across ", length(unique(df$response_id)), " unique respondents"))
    
```
<br>
<br>

**Table: How is the DHPC (i.e. Dear Pharmacist letter) disseminated to pharmacists and technicians in your pharmacy?**

```{r}

  data |>
    filter(finished == "Yes") |>
    select(starts_with("q4_7_") & !contains("text")) |> 
  tbl_summary(
    missing = "ifany", 
    missing_text = "Missing values",
    # type = list(
    #   everything() ~ "categorical"
    #   ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) 
  
```
<br>
<br>

### Free text

```{r}

  data |> select(q4_7_7_text, finished) |> na.omit()

```
<br>
<br>

## Q4.8

**Figure: If pharmacist or other colleagues are on leave how is the information from the DHPC communicated to them?**

```{r}

  df <- data |>
    filter(!is.na(q4_8)) |>
    select(response_id, starts_with("q4_t8_")) |> 
    pivot_longer(-c(response_id)) |>
    filter(value != "No") |>
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n))
    

  df |>
  ggplot(aes(x = value, fill = n)) +
    geom_bar() +
    scale_fill_viridis(
      guide = "none", option = "A", begin = 0.4, discrete = FALSE
      ) +
    coord_flip() +
    xlab("") +
    ylab("Number of respondent's endorsing") +
    theme(panel.grid = element_blank()) +
    scale_x_discrete(labels = function(x) str_wrap(x, 30)) +
    labs(caption= paste0("n = ", nrow(df), " total endorsements across ", length(unique(df$response_id)), " unique respondents"))
    
```
<br>
<br>

**Table: If pharmacist or other colleagues are on leave how is the information from the DHPC communicated to them?**

```{r}

  data |>
    filter(finished == "Yes") |>
    select(starts_with("q4_8_") & !contains("text")) |> 
  tbl_summary(
    missing = "ifany", 
    missing_text = "Missing values",
    # type = list(
    #   everything() ~ "categorical"
    #   ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) 
  
```
<br>
<br>

### Free text

```{r}

  data |> select(q4_8_4_text, finished) |> na.omit()

```
<br>
<br>

## Q4.9

**Table: Is the information from the DHPC communicated to new staff/pharmacy locums?**

```{r}

  data |>
    filter(finished == "Yes") |>
    select(q4_9) |> 
  tbl_summary(
    missing = "ifany", 
    missing_text = "Missing values",
    # type = list(
    #   everything() ~ "categorical"
    #   ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) 
  
```
<br>
<br>

### Free text

```{r}

  data |> select(q4_9_3_text, finished) |> na.omit()

```
<br>
<br>

## Q4.10

**Figure: If the DHPC is communicated to new staff/pharmacy locums how is this done?**

```{r}

  df <- data |>
    filter(!is.na(q4_10)) |>
    select(response_id, starts_with("q4_t10_")) |> 
    pivot_longer(-c(response_id)) |>
    filter(value != "No") |>
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n))
    

  df |>
  ggplot(aes(x = value, fill = n)) +
    geom_bar() +
    scale_fill_viridis(
      guide = "none", option = "A", begin = 0.4, discrete = FALSE
      ) +
    coord_flip() +
    xlab("") +
    ylab("Number of respondent's endorsing") +
    theme(panel.grid = element_blank()) +
    scale_x_discrete(labels = function(x) str_wrap(x, 30)) +
    labs(caption= paste0("n = ", nrow(df), " total endorsements across ", length(unique(df$response_id)), " unique respondents"))
    
```
<br>
<br>

**Table: If the DHPC is communicated to new staff/pharmacy locums how is this done?**

```{r}

  data |>
    filter(finished == "Yes") |>
    select(starts_with("q4_10_") & !contains("text")) |> 
  tbl_summary(
    missing = "ifany", 
    missing_text = "Missing values",
    # type = list(
    #   everything() ~ "categorical"
    #   ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) 
  
```
<br>
<br>

### Free text

```{r}

  data |> select(q4_10_6_text, finished) |> na.omit()

```
<br>
<br>

## Q4.11

**Figure: Are there any barriers that prevent you from implementing DHPC recommendations in your pharmacy?**

```{r}

  df <- data |>
    filter(!is.na(q4_11)) |>
    select(response_id, starts_with("q4_t11_")) |> 
    pivot_longer(-c(response_id)) |>
    filter(value != "No") |>
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n))
    

  df |>
  ggplot(aes(x = value, fill = n)) +
    geom_bar() +
    scale_fill_viridis(
      guide = "none", option = "A", begin = 0.4, discrete = FALSE
      ) +
    coord_flip() +
    xlab("") +
    ylab("Number of respondent's endorsing") +
    theme(panel.grid = element_blank()) +
    scale_x_discrete(labels = function(x) str_wrap(x, 30)) +
    labs(caption= paste0("n = ", nrow(df), " total endorsements across ", length(unique(df$response_id)), " unique respondents"))
    
```
<br>
<br>

**Table: Are there any barriers that prevent you from implementing DHPC recommendations in your pharmacy?**

```{r}

  data |>
    filter(finished == "Yes") |>
    select(starts_with("q4_11_") & !contains("text")) |> 
  tbl_summary(
    missing = "ifany", 
    missing_text = "Missing values",
    # type = list(
    #   everything() ~ "categorical"
    #   ), 
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) 
  
```
<br>
<br>

### Free text

```{r}

  data |> select(q4_11_8_text, finished) |> na.omit()

```
<br>
<br>

```{r sysinfo}

  DescTools::SysInfo()

```