---
title: ''
author: ''
date: ''
output: 
  html_document:
    df_print: paged
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
    theme: "flatly"
    code_download: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}

  knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                        fig.width  = 6 * 1.67, fig.height = 6)

```

```{r}

  library(descr)
  library(tidyverse)
  library(viridis)
  library(testthat)
  library(knitr)
  library(plotly)
  library(gtsummary)
  library(patchwork)
  library(janitor)
  library(likert)
  
```

```{r}

# Set colors/theme for plots

  col1 <- viridis(1, option = "A", end = 0.9, dir = -1)
  col2 <- viridis(1, option = "A")
# col3 <- viridis(1, option = "A", begin = 0.4)
  col3 <- "#21091F"
  col4 <- viridis(1, option = "A", begin = 0.6)
  col5 <- viridis(1, option = "A", begin = 0.1)

  my_theme <- theme_minimal() +
    theme(
      panel.background = element_rect(fill = col2), 
      axis.text = element_text(color = col1),
      axis.title = element_text(color = col1),
      plot.background = element_rect(fill = col2), 
      legend.background = element_rect(fill = col2), 
      legend.text = element_text(color = col4), 
      legend.title = element_text(color = col4), 
      axis.ticks = element_line(color = col1), 
      title = element_text(color = col1), 
      panel.grid = element_line(color = col3), 
      strip.text = element_text(color = col1), 
      plot.subtitle = element_text(color = col1),
      plot.caption = element_text(hjust = 0)
      )
  
  theme_set(my_theme)
  
```

```{r}

  load("data/data.RData") 

  expect_equal(nrow(data), length(unique(data$response_id)))
  
  start_n <- nrow(data)

```

```{r}

  finished_n <- table(data$finished)["Yes"]
  finished_p <- round(finished_n / nrow(data) * 100, 1)
  consent_n <- table(data$qid43)["Yes"]
  consent_p <- round(consent_n / nrow(data) * 100, 1)

```

# Survey completion

There are `r start_n` total responses in the survey dataset. Of these, `r finished_n` finished the survey (`r finished_p`%). 

Across all `r start_n` respondents, `r consent_n` provided consent (`r consent_p`%), including 100% of those who completed the survey.

Survey start dates ranged from `r min(as.Date(data$start_date))` to `r max(as.Date(data$start_date))`. 

**Figure: Survey accrual**

```{r}

  data |>
    arrange(start_date) |>
    group_by(finished) |>
    mutate(obs = 1, cum_obs = cumsum(obs)) |> 
    ungroup() |>
  ggplot(aes(x = start_date, y = cum_obs, color = finished)) +
    geom_step(size = 1) +
    scale_color_viridis(
      "Finished?", option = "A", begin = 0.6, discrete = TRUE
      ) +
    xlab("Date participants started the survey") +
    ylab("Cummulative number of participants") +
    theme(legend.position = "bottom") +
    labs(caption = paste0("n = ", nrow(data)))

```
<br>
<br>

Survey accrual was similar for those who did vs didn't finish the survey. 

**Figure: Survey progress for those that didn't finish the survey**

```{r}

  data |>
    filter(finished == "No") |>
  ggplot(aes(x = progress)) +
    geom_histogram(fill = col4) +
    xlab("Survey progress (%)") +
    ylab("Number of participants") +
    labs(caption = paste0("n = ", nrow(data) - finished_n))

```
<br>
<br>

**Figure: Minutes spent on the survey for those that finished**

```{r}

  data |>
    filter(finished == "Yes") |>
  ggplot(aes(x = duration_in_minutes)) +
    scale_x_log10() +
    geom_histogram(fill = col4) +
    xlab("Minutes spent on the survey") +
    ylab("Number of participants") +
    labs(caption = paste0("n = ", finished_n))

```
<br>
<br>

**Figure: Minutes spent on the survey for those that didn't finish**

```{r}

  data |>
    filter(finished == "No") |>
  ggplot(aes(x = duration_in_minutes)) +
    scale_x_log10() +
    geom_histogram(fill = col4) +
    xlab("Minutes spent on the survey") +
    ylab("Number of participants") +
    labs(caption = paste0("n = ", nrow(data) - finished_n))

```
<br>
<br>

**Figure: Number of non-missing values across all survey variables for finishers**

```{r}

  data_frame(
    n_obs = unlist(map(
      data[data$finished == "Yes",], function(x) table(is.na(x))["FALSE"]
      )),
    variable_name = names(data)
    ) |>
    mutate(variable_name = reorder(factor(variable_name), n_obs)) |> 
    # filter(n_obs != finished_n) |> 
    mutate(q = as.numeric(gsub("q", "", str_split_i(variable_name, "_", 1)))) |>
  ggplot(aes(x = variable_name, y = n_obs, fill = n_obs)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    labs(
      x = "Variable", y = "N non-missing values for variables with any missings"
      ) +
    facet_wrap(~q, scales = "free_y") +
    scale_fill_viridis(guide = "none", option = "A", begin = 0.3) +
    theme(
      panel.grid = element_blank(), 
      panel.background = element_rect(fill = NA, color = col4), 
      axis.text.y = element_text(size = 5)
      ) 

```
<br>
<br>

**Figure: Number of non-missing values across all survey variables for non-finishers**

```{r}

  data_frame(
    n_obs = unlist(map(
      data[data$finished == "No",], function(x) table(is.na(x))["FALSE"]
      )),
    variable_name = names(data)
    ) |>
    mutate(variable_name = reorder(factor(variable_name), n_obs)) |> 
    mutate(q = as.numeric(gsub("q", "", str_split_i(variable_name, "_", 1)))) |>
  ggplot(aes(x = variable_name, y = n_obs, fill = n_obs)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    labs(
      x = "Variable", y = "N non-missing values for variables with any missings"
      ) +
    facet_wrap(~q, scales = "free_y") +
    scale_fill_viridis(guide = "none", option = "A", begin = 0.3) +
    theme(
      panel.grid = element_blank(), 
      panel.background = element_rect(fill = NA, color = col4), 
      axis.text.y = element_text(size = 5)
      ) 

```
<br>
<br>

Finishers vs non-finishers on Q1-Q7

```{r}

  data |>
    select(finished, q2:q5, q7) |> 
  tbl_summary(
    by = finished,
    missing = "ifany", 
    missing_text = "Missing values",
    type = list(q4 ~ "categorical"),
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) |>
    modify_spanning_header(c(stat_1, stat_2) ~ "**Finished survey?**") |>
    add_p(test = list(
      all_categorical() ~ "chisq.test"
      ))
```

`r attr(data$q1, "label")`
 
```{r}

  data |>
    group_by(finished) |>
    mutate(n_f = n()) |>
    group_by(finished, q1) |>
    mutate(n_q1 = n()) |>
    mutate(q1_prop = n_q1/n_f) |>
    select(q1, finished, q1_prop) |>
    distinct() |>
    ungroup() |>
    mutate(q1 = reorder(factor(q1), q1_prop)) |>
  ggplot(aes(x = q1, y = q1_prop, group = finished, fill = finished)) +
    geom_bar(stat = "identity", position = "dodge") +
    scale_fill_viridis(
      "Finished\nsurvey", option = "A", begin = 0.4, discrete = TRUE
      ) +
    coord_flip() +
    xlab("") +
    ylab("Proportion of respondents") +
    theme(legend.position = "bottom")

```


`r attr(data$q6, "label")`
 
```{r}

  data |>
    group_by(finished) |>
    mutate(n_f = n()) |>
    group_by(finished, q6) |>
    mutate(n_q6 = n()) |>
    mutate(q6_prop = n_q6/n_f) |>
    select(q6, finished, q6_prop) |>
    distinct() |>
    ungroup() |>
    mutate(q6 = reorder(factor(q6), q6_prop)) |>
  ggplot(aes(x = q6, y = q6_prop, group = finished, fill = finished)) +
    geom_bar(stat = "identity", position = "dodge") +
    scale_fill_viridis(
      "Finished\nsurvey", option = "A", begin = 0.4, discrete = TRUE
      ) +
    coord_flip() +
    xlab("") +
    ylab("Proportion of respondents") +
    theme(legend.position = "bottom")

```

# Results

## (Q1-7) Repondent characteristics

From this point forward the dataset it limited to the `r finished_n` participants who completed the survey. 

```{r}

  data <- filter(data, finished == "Yes")

```

#### Table: Respondent characteristics

```{r}

  data |>
    select(q2:q5, q7) |> 
  tbl_summary(
    missing = "ifany", 
    missing_text = "Missing values",
    type = list(q4 ~ "categorical"),
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) 

```

#### Figure: `r attr(data$q1, "label")` (Q1)
 
```{r}

  data |>
    select(q1) |>
    na.omit() |>
    group_by(q1) |>
    mutate(n_q1 = n()) |>
    mutate(q1_prop = n_q1/nrow(data)) |>
    select(q1, q1_prop) |>
    distinct() |>
    ungroup() |>
    mutate(q1 = reorder(factor(q1), q1_prop)) |>
  ggplot(aes(x = q1, y = q1_prop, fill = q1_prop)) +
    geom_bar(stat = "identity", position = "dodge") +
   scale_fill_viridis(guide = "none", option = "A", begin = 0.4) +
    coord_flip() +
    xlab("") +
    ylab("Proportion of respondents") +
    theme(legend.position = "bottom")

```

#### Table: `r attr(data$q1, "label")` (Q1)

```{r}

  data |>
    select(q1) |>
    group_by(q1) |>
    mutate(n_q1 = n()) |>
    mutate(q1_prop = n_q1/nrow(data)) |>
    select(q1, q1_prop) |>
    distinct() |>
    ungroup() |>
    mutate(q1 = reorder(factor(q1), q1_prop)) |>
  tbl_summary(
    missing = "ifany", 
    missing_text = "Missing values",
    type = list(q1 ~ "categorical"),
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) 
```

#### Figure: `r attr(data$q2, "label")` (Q2)

```{r}

  ggplot(data, aes(x = q2)) +
    geom_bar(fill = col4) +
    coord_flip() +
    xlab("") +
    ylab("Number of respondents") +
    theme(panel.grid = element_blank())

```

#### Figure: `r attr(data$q5, "label")` (Q5)

```{r}

  ggplot(data, aes(x = q5)) +
    geom_bar(fill = col4) +
    coord_flip() +
    xlab("") +
    ylab("Number of respondents") +
    theme(panel.grid = element_blank())

```

#### Figure: `r attr(data$q6, "label")` (Q6)
 
```{r}

  # unique(data$q6)[order(unique(data$q6))]
  all_countries <- gsub(" and the|\\\n| and", ",", data$q6) %>%
    gsub(" - uk", "", .) |>
    tolower() |>
    str_split(",") |>
    unlist() |>
    trimws() |>
    str_to_title() 

  all_countries[all_countries == "Uk"] <- "UK"
  all_countries[all_countries == "England"] <- "UK"
  all_countries[all_countries == "Usa"] <- "USA"
  all_countries[all_countries == "Us"] <- "USA"
  all_countries[all_countries == "Ksa"] <- "KSA"
  all_countries[all_countries == "United States"] <- "USA"
  all_countries[all_countries == ""] <- NA
  all_countries[grepl("Canada", all_countries)] <- NA

  
  all_countries <- c(
    all_countries, "Canada", "South Africa", "India", "China"
    ) |>
    na.omit()
  
  n_r <- length(data$q6[!is.na(data$q6)])
  n_c <- length(all_countries)

  data_frame(country = all_countries) |>
    group_by(country) |>
    mutate(n_q6 = n()) |>
    select(country, n_q6) |>
    distinct() |>
    ungroup() |>
    mutate(country = reorder(factor(country), n_q6)) |> 
  ggplot(aes(x = country, y = n_q6, fill = n_q6)) +
    geom_bar(stat = "identity", position = "dodge") +
   scale_fill_viridis(guide = "none", option = "A", begin = 0.4) +
    coord_flip() +
    xlab("") +
    ylab("Number of repondents working on trials in this country") +
    theme(legend.position = "bottom") +
    labs(
      caption = paste0(n_c, " countries, across ", n_r, " respondents")
      ) +
    theme(panel.grid = element_blank())

```

#### Table: `r attr(data$q6, "label")` (Q6)

```{r}

  data_frame(country = all_countries) |>
    na.omit() |>
    group_by(country) |>
    mutate(n_q6 = n()) |>
    ungroup() |>
    mutate(country = reorder(factor(country), n_q6))  |>
    select(-n_q6) |>
  tbl_summary(
    missing = "ifany", 
    missing_text = "Missing values",
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) 
```

## (Q8) Trial Status

#### Figure: Number of current trials for each respondent

```{r}

  data |>
    select(response_id, starts_with("q8")) |> 
    pivot_longer(-response_id) |>
    mutate(name = gsub("q8_", "", name)) |>
    na.omit() |>
  ggplot(aes(x = name, fill = name)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = TRUE, begin = 0.4
      ) +
    xlab("Current number of trials") +
    ylab("Number of respondents")
      
```

#### Figure: Status of all current trials

```{r}

  data |>
    select(response_id, starts_with("q8")) |>
    pivot_longer(-response_id) |>
    mutate(name = gsub("q8_", "", name)) |>
    na.omit() |>
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(x = value, fill = value)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = TRUE, begin = 0.4
      ) +
    xlab("") +
    ylab("Number of trials")
      
```

#### Figure: Number and status of all current trials, by respondent

```{r}

  data |>
    select(response_id, starts_with("q8")) |> 
    pivot_longer(-response_id) |>
    mutate(name = gsub("q8_", "", name)) |>
    na.omit() |>
    arrange(response_id, value) |>
    group_by(response_id) |>
    mutate(flag = 1, trial = cumsum(flag), n_trials = max(trial)) |>
    ungroup() |>
    mutate(response_id = reorder(factor(response_id), n_trials)) |>
  ggplot(aes(x = trial, y = response_id, fill = value)) +
    geom_tile() +
    scale_fill_viridis("", option = "A", discrete = TRUE, begin = 0.4) +
    xlab("Trial") +
    ylab("Respondent") +
    theme(
      axis.text.y = element_blank(),
      legend.position = "bottom", 
      panel.grid = element_blank()
      )
  
```

#### Table: `r attr(data$q8_1, "label")`-4

```{r}

  data |>
    select(starts_with("q8")) |>
  tbl_summary(
    missing = "ifany",
    missing_text = "Missing values",
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) 

```

```{r, eval = FALSE}

#### Missing pattern for q8, looks file

  data |>
    select(response_id, starts_with("q8")) |>
    mutate(
      m_8_1 = !is.na(q8_1), 
      m_8_2 = !is.na(q8_2),
      m_8_4 = !is.na(q8_3), 
      m_8_5 = !is.na(q8_4)
      )|>
    select(response_id, starts_with("m_8")) |>
    pivot_longer(-response_id) |> 
    group_by(response_id) |>
    mutate(trials = sum(value)) |>
    ungroup() |>
    mutate(response_id = reorder(factor(response_id), trials)) |>
  ggplot(aes(x = name, y = response_id, fill = value)) +
    geom_tile() +
    scale_fill_viridis(
      "Not missing", option = "A", discrete = TRUE, begin = 0.4
      ) +
    xlab("Trial") +
    ylab("Respondent") +
    theme(
      axis.text.y = element_blank(),
      legend.position = "bottom", 
      panel.grid = element_blank()
      )
    
```

## (Q9) Current and previous roles working on childhood obesity prevention trials 

#### Figure: Current and previous roles working on childhood obesity prevention trials across all respondents

```{r}

  levs <- names(select(data, starts_with("q9"), -contains("text")))
# meta_data$labels[meta_data$var_name %in% levs]
  labs <- c(
    "PI", "PI", "Co-I", "Co-I", "Researcher", "Researcher", "RA", "RA", 
    "Trial statistician", "Trial statistician", 
    "Trial coordinator", "Trial coordinator", "Site manager", "Site manager",
    "HCP", "HCP", "Committee member", "Committee member", "Other", "Other"
    )
  df <- data |>
    select(response_id, starts_with("q9"), -contains("text")) |>
    map_df(as.character) |>
    pivot_longer(-response_id, names_to = "role", values_to = "type") |>
    filter(type != "0") |>
    na.omit() |>
    mutate(role = factor(role, levels = levs, labels = labs)) |>
    group_by(role) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(role = reorder(factor(role), n)) 
  
  n_r <- length(unique(df$response_id))
  n_c <- nrow(df)

  df |>
  ggplot(aes(x = role, fill = type)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis("", option = "A", discrete = TRUE, begin = 0.4) +
    theme(
      panel.grid = element_blank(), 
      legend.position = "bottom"
      ) +
    labs(y = "Number of respondents", x = "") + 
    labs(
      caption = paste0(n_c, " roles, across ", n_r, " respondents")
      ) 

```

#### Free text

```{r}

  data$q9_10_text |> 
  na.omit() |>
  paste(collapse = "; ")

```

## (Q10) Methods for identifying outcomes 

#### Figure: Methods for identifying outcomes as reported across all respondents

```{r}

  levs <- names(select(data, starts_with("q10"), -contains("text")))
  x <- unlist(
    str_split(meta_data$labels[meta_data$var_name %in% levs], "Choice - ")
    )
  labs <- x[1:length(x) %% 2 == 0]

  df <- data |>
    select(response_id, starts_with("q10"), -contains("text")) |> 
    map_df(as.character) |>
    pivot_longer(-response_id, names_to = "source", values_to = "value") |>
    filter(value != "0") |>
    na.omit() |> 
    mutate(source = factor(source, levels = levs, labels = labs)) |>
    group_by(source) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(source = reorder(factor(source), n)) 
  
  n_r <- length(unique(df$response_id))
  n_c <- nrow(df)

  df |>
  ggplot(aes(x = source, fill = n)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(guide = "none", option = "A", begin = 0.4) +
    theme(
      panel.grid = element_blank(), 
      legend.position = "bottom"
      ) +
    labs(y = "Number of respondents", x = "") + 
    labs(
      caption = paste0(n_c, " sources, across ", n_r, " respondents")
      ) 

```

#### Free text

```{r}

  data$q10_12_text |> 
  na.omit() |>
  paste(collapse = "; ")

```

## (Q11 & 12) Familiarity with core outcome sets 

Among the `r length(unique(data$response_id))` respondents, `r length(data$q11[data$q11 == "Yes"])` indicated they had heard of, or were familiar with, core outcome sets prior to taking the survey. 

#### Figure: Sources of previous exposure to core outcome sets

```{r}

  levs <- names(select(data, starts_with("q12"), -contains("text")))
  x <- unlist(
    str_split(meta_data$labels[meta_data$var_name %in% levs], "Choice - ")
    )
  labs <- x[1:length(x) %% 2 == 0]

  df <- data |>
    select(response_id, starts_with("q12"), -contains("text")) |> 
    map_df(as.character) |>
    pivot_longer(-response_id, names_to = "source", values_to = "value") |>
    filter(value != "0") |>
    na.omit() |> 
    mutate(source = factor(source, levels = levs, labels = labs)) |>
    group_by(source) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(source = reorder(factor(source), n)) 
  
  n_r <- length(unique(df$response_id))
  n_c <- nrow(df)

  df |>
  ggplot(aes(x = source, fill = n)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(guide = "none", option = "A", begin = 0.4) +
    theme(
      panel.grid = element_blank(), 
      legend.position = "bottom"
      ) +
    labs(y = "Number of respondents", x = "") + 
    labs(
      caption = paste0(n_c, " sources, across ", n_r, " respondents")
      ) 

```

Note: I don't see an actual open text variable associated with this set of responses. 

## (Q13) Familarity with existing core outcomes sets for childhood obesity trials 

#### Table: Familarity with existing core outcomes sets for childhood obesity trials

```{r}

  data |>
    select(q13) |>
  tbl_summary(
    missing = "ifany",
    missing_text = "Missing values",
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) 

```

## (Q14) Sources of familiarity with existing core outcomes sets for childhood obesity 

#### Figure: Sources of previous exposure to core outcome sets

```{r}

  levs <- names(select(data, starts_with("q14"), -contains("text")))
  labs <- meta_data$labels[meta_data$var_name %in% levs]

  df <- data |>
    select(response_id, starts_with("q14"), -contains("text")) |> 
    map_df(as.character) |>
    pivot_longer(-response_id, names_to = "source", values_to = "value") |>
    filter(value != "0") |>
    na.omit() |> 
    mutate(source = factor(source, levels = levs, labels = labs)) |> 
    separate_wider_delim(
      source, delim = " - ", names = c("source", "cos"), cols_remove = TRUE
      ) |>
    group_by(source) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(source = reorder(factor(source), n, decreasing = FALSE))
  
  n_r <- length(unique(df$response_id))
  n_c <- nrow(df)

  df |>
  ggplot(aes(x = source, fill = cos)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      "", option = "A", begin = 0.4, discrete = TRUE
      ) +
    facet_wrap(~cos) +
    theme(
      panel.grid = element_blank(), 
      legend.position = "bottom"
      ) +
    labs(y = "Number of respondents", x = "") + 
    labs(
      caption = paste0(n_c, " sources, across ", n_r, " respondents")
      ) 

```

```{r}

  attr(df$source, "label") <- "Source"

  df |>
    select(-response_id, -value, -n) |>
  tbl_summary(
    by = cos, 
    missing = "ifany",
    missing_text = "Missing values",
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) |>
    add_n() |>
    modify_footnote(n ~ paste0(n_c, " sources endorsed by ", n_r, " respondents"))

```

Note: No actual open text field for "other". 

## (Q15) Barriers to using childhood obesity prevention core outcome set(s) in a trial 

#### Figure: Barriers to using childhood obesity prevention core outcome set(s) in a trial

```{r}

  levs <- names(select(data, starts_with("q15"), -contains("text")))
  labs <- meta_data$labels[meta_data$var_name %in% levs]

  df <- data |>
    select(response_id, starts_with("q15"), -contains("text")) |> 
    map_df(as.character) |>
    pivot_longer(-response_id, names_to = "barrier", values_to = "value") |>
    filter(value != "0") |>
    na.omit() |> 
    mutate(barrier = factor(barrier, levels = levs, labels = labs)) |> 
    separate_wider_delim(
      barrier, delim = " - ", names = c("barrier", "cos"), cols_remove = TRUE
      ) |>
    group_by(barrier) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(barrier = reorder(factor(barrier), n, decreasing = FALSE))
  
  n_r <- length(unique(df$response_id))
  n_c <- nrow(df)

  df |>
  ggplot(aes(x = barrier, fill = cos)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      "", option = "A", begin = 0.4, discrete = TRUE
      ) +
    facet_wrap(~cos) +
    theme(
      panel.grid = element_blank(), 
      legend.position = "bottom"
      ) +
    labs(y = "Number of respondents", x = "") + 
    labs(
      caption = paste0(n_c, " barriers, across ", n_r, " respondents")
      ) 

```

```{r}

  attr(df$barrier, "label") <- "Barrier"

  df |>
    select(-response_id, -value, -n) |>
  tbl_summary(
    by = cos, 
    missing = "ifany",
    missing_text = "Missing values",
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) |>
    add_n() |>
    modify_footnote(n ~ paste0(n_c, " sources endorsed by ", n_r, " respondents"))

```

#### Free text

```{r}

  data$q15_16_text |> 
  na.omit() |>
  paste(collapse = "; ")

```

## (Q16) Faciliators to using childhood obesity prevention core outcome set(s) in a trial 

#### Figure: Faciliators to using childhood obesity prevention core outcome set(s) in a trial

```{r}

  levs <- names(select(data, starts_with("q16"), -contains("text")))
  labs <- meta_data$labels[meta_data$var_name %in% levs]

  df <- data |>
    select(response_id, starts_with("q16"), -contains("text")) |> 
    map_df(as.character) |>
    pivot_longer(-response_id, names_to = "facilitator", values_to = "value") |>
    filter(value != "0") |>
    na.omit() |> 
    mutate(facilitator = factor(facilitator, levels = levs, labels = labs)) |> 
    separate_wider_delim(
      facilitator, delim = " - ", names = c("facilitator", "cos"), cols_remove = TRUE
      ) |>
    group_by(facilitator) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(facilitator = reorder(factor(facilitator), n, decreasing = FALSE))
  
  n_r <- length(unique(df$response_id))
  n_c <- nrow(df)

  df |>
  ggplot(aes(x = facilitator, fill = cos)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      "", option = "A", begin = 0.4, discrete = TRUE
      ) +
    facet_wrap(~cos) +
    theme(
      panel.grid = element_blank(), 
      legend.position = "bottom"
      ) +
    labs(y = "Number of respondents", x = "") + 
    labs(
      caption = paste0(n_c, " facilitators, across ", n_r, " respondents")
      ) 

```

```{r}

  attr(df$facilitator, "label") <- "Facilitator"

  df |>
    select(-response_id, -value, -n) |>
  tbl_summary(
    by = cos, 
    missing = "ifany",
    missing_text = "Missing values",
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) |>
    add_n() |>
    modify_footnote(n ~ paste0(n_c, " facilitators endorsed by ", n_r, " respondents"))

```

#### Free text

```{r}

  data$q16_19_text |> 
  na.omit() |>
  paste(collapse = "; ")

```

## (Q17) Sources to identify outcomes in childhood obesity prevention trials 

#### Figure: Sources to identify outcomes in childhood obesity prevention trials

```{r}

  levs <- names(select(data, starts_with("q17"), -contains("text")))
  labs <- meta_data$labels[meta_data$var_name %in% levs]

  df <- data |>
    select(response_id, starts_with("q17"), -contains("text")) |> 
    map_df(as.character) |>
    pivot_longer(-response_id, names_to = "source", values_to = "value") |>
    filter(value != "0") |>
    na.omit() |> 
    mutate(source = factor(source, levels = levs, labels = labs)) |> 
    group_by(source) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(source = reorder(factor(source), n, decreasing = TRUE))
  
  n_r <- length(unique(df$response_id))
  n_c <- nrow(df)

  df |>
  ggplot(aes(x = source, fill = n)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(guide = "none", option = "A", begin = 0.4) +
    theme(
      panel.grid = element_blank(), 
      legend.position = "bottom"
      ) +
    labs(y = "Number of respondents", x = "") + 
    labs(
      caption = paste0(n_c, " sources, across ", n_r, " respondents")
      ) 

```

```{r}

  attr(df$source, "label") <- "Sources"

  df |>
    select(-response_id, -value, -n) |>
  tbl_summary(
    missing = "ifany",
    missing_text = "Missing values",
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) |>
    add_n() |>
    modify_footnote(n ~ paste0(n_c, " sources endorsed by ", n_r, " respondents"))

```


Note: No actual free text field for "other" responses. 

## (Q18) Currently planned/used outcomes 

#### Figure: Currently planned/used outcomes in childhood obesity prevention interventions.

```{r}

  levs <- names(select(data, starts_with("q18"), -contains("text")))
  x <- unlist(
    str_split(meta_data$labels[meta_data$var_name %in% levs], "Choice - ")
    )
  labs <- x[1:length(x) %% 2 == 0]

  df <- data |>
    select(response_id, starts_with("q18"), -contains("text")) |> 
    map_df(as.character) |>
    pivot_longer(-response_id, names_to = "outcome", values_to = "value") |>
    filter(value != "0") |>
    na.omit() |> 
    mutate(outcome = factor(outcome, levels = levs, labels = labs)) |>
    group_by(outcome) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(outcome = reorder(factor(outcome), n))
  
  n_r <- length(unique(df$response_id))
  n_c <- nrow(df)

  df |>
  ggplot(aes(x = outcome, fill = n)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(guide = "none", option = "A", begin = 0.4) +
    theme(
      panel.grid = element_blank(), 
      legend.position = "bottom"
      ) +
    labs(y = "Number of respondents", x = "") + 
    labs(
      caption = paste0(n_c, " outcomes, across ", n_r, " respondents")
      ) 

```

#### Free text

```{r}

  data$q18_11_text |> 
  na.omit() |>
  paste(collapse = "; ")

```

## (Q19) Administration 

#### Figure: Route and method of administration across all responses

```{r}

  df <- data |>
    select(response_id, starts_with("q19") & !contains("_6")) |>
    pivot_longer(-response_id) |>
    na.omit()

  df$name[grepl("q19_1_", df$name)] <- "In person"
  df$name[grepl("q19_2_", df$name)] <- "Electronically"
  df$name[grepl("q19_3_", df$name)] <- "By phone"
  df$name[grepl("q19_4_", df$name)] <- "Via post"
  df$name[grepl("q19_5_", df$name)] <- "Combination"

  attr(df$name, "label") <- "Route"
  attr(df$value, "label") <- "Method"
  
  df |>
    group_by(value, name) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(y = value, x = name, color = n)) +
    geom_jitter(alpha = 0.8) +
    geom_tile(fill = NA) +
    geom_text(
      aes(label = n), 
      position = position_nudge(x = 0.4, y = -0.4),
      color = col1,
      size = 3
      ) +
    scale_color_viridis(
      guide = "none", option = "A", discrete = FALSE, begin = 0.5
      ) +
    xlab("") +
    ylab("") +
    theme(panel.grid = element_blank()) +
    ggtitle("How have you/do you plan to administer\nthe outcome measurement instruments in a trial?") +
    labs(caption = "n = 288 total reponses across 45 respondents")
  
  # ggsave("plots/q19.png", device = "png", 
  #   scale = 0.6, units = "cm", 
  #   width = 33.87, height = 19.05, dpi = 300
  #   )
    
```

#### Table: Route and method of administration across all responses

```{r}

  df |>
    select(-response_id) |>
  tbl_cross(
    margin = c("column", "row"), 
    percent = "cell"
  )

```

#### Figure: Route and method of administration across all responses

```{r}

  g1 <- df |>
    ggplot(aes(x = value, fill = name)) +
      geom_bar() +
      scale_fill_viridis(
        "", option = "A", begin = 0.4, discrete = TRUE
        ) +
      coord_flip() +
      ylab("Number of responses") +
      xlab("")

  g2 <- df |>
    ggplot(aes(x = value, fill = name)) +
      geom_bar(position = "fill") +
      scale_fill_viridis(
        "", option = "A", begin = 0.4, discrete = TRUE
        ) +
      coord_flip() +
      ylab("Proportion of responses") +
      xlab("") +
      theme(axis.text.y = element_blank())
  
  g1 + g2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")

```

#### Figure: Method of administration across all responses

```{r}

  df |>
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(x = value, fill = n)) +
    geom_bar() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = FALSE, begin = 0.5
      ) +
    coord_flip() +
    xlab("") +
    ylab("Responses") +
    labs(caption = "n = 288 total reponses across 45 respondents")
  
```

#### Figure: Route of administration across all responses

```{r}

  df |>
    group_by(name) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(name = reorder(factor(name), n)) |>
  ggplot(aes(x = name, fill = n)) +
    geom_bar() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = FALSE, begin = 0.5
      ) +
    coord_flip() +
    xlab("") +
    ylab("Responses")  +
    labs(caption = "n = 288 total reponses across 45 respondents")
  
```

#### Figure: Method of administration - In person

```{r}

  data |>
    select(response_id, starts_with("q19_1")) |> 
    pivot_longer(-response_id) |>
    mutate(name = gsub("q19_1_", "", name)) |>
    na.omit() |> 
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(x = value, fill = value)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = TRUE, begin = 0.4
      ) +
    xlab("") +
    ylab("Number of trials")
      
```

#### Figure: Method of administration - Electronically

```{r}

  data |>
    select(response_id, starts_with("q19_2")) |> 
    pivot_longer(-response_id) |>
    mutate(name = gsub("q19_2_", "", name)) |>
    na.omit() |> 
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(x = value, fill = value)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = TRUE, begin = 0.4
      ) +
    xlab("") +
    ylab("Number of trials")
      
```

#### Figure: Method of administration - By phone

```{r}

  data |>
    select(response_id, starts_with("q19_3")) |> 
    pivot_longer(-response_id) |>
    mutate(name = gsub("q19_3_", "", name)) |>
    na.omit() |> 
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(x = value, fill = value)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = TRUE, begin = 0.4
      ) +
    xlab("") +
    ylab("Number of trials")
      
```

#### Figure: Method of administration - Via post

```{r}

  data |>
    select(response_id, starts_with("q19_4")) |> 
    pivot_longer(-response_id) |>
    mutate(name = gsub("q19_4_", "", name)) |>
    na.omit() |> 
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(x = value, fill = value)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = TRUE, begin = 0.4
      ) +
    xlab("") +
    ylab("Number of trials")
      
```

#### Figure: Method of administration - Combination

```{r}

  data |>
    select(response_id, starts_with("q19_5")) |> 
    pivot_longer(-response_id) |>
    mutate(name = gsub("q19_5_", "", name)) |>
    na.omit() |> 
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(x = value, fill = value)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = TRUE, begin = 0.4
      ) +
    xlab("") +
    ylab("Number of trials")
      
```

#### Free text

```{r}

  data |>
    select(starts_with("q19_6")) |> 
    remove_empty() |> 
    unlist() |>
    unique() 

```

## (Q20) Location 

#### Figure: Method and setting of administration across all responses

```{r}

  df <- data |>
    select(response_id, starts_with("q20") & !contains("_7")) |>
    pivot_longer(-response_id) |>
    na.omit()

  df$name[grepl("q20_1_", df$name)] <- "Healthcare"
  df$name[grepl("q20_2_", df$name)] <- "Home"
  df$name[grepl("q20_3_", df$name)] <- "Community"
  df$name[grepl("q20_4_", df$name)] <- "Education"
  df$name[grepl("q20_5_", df$name)] <- "Academic/research"
  df$name[grepl("q20_6_", df$name)] <- "Combination"

  attr(df$name, "label") <- "Setting"
  attr(df$value, "label") <- "Method"

  df |>
    group_by(value, name) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(y = value, x = name, color = n)) +
    geom_jitter(alpha = 0.8) +
    geom_tile(fill = NA) +
    geom_text(
      aes(label = n), 
      position = position_nudge(x = 0.4, y = -0.4),
      color = col1,
      size = 3
      ) +
    scale_color_viridis(
      guide = "none", option = "A", discrete = FALSE, begin = 0.5
      ) +
    xlab("Setting") +
    ylab("") +
    theme(panel.grid = element_blank()) +
    ggtitle("Where have you/will you collect data using\noutcome measurement instruments in your trial?") +
    labs(caption = "n = 347 total reponses across 45 respondents")
  
  # ggsave("plots/q20.png", device = "png", 
  #   scale = 0.6, units = "cm", 
  #   width = 33.87, height = 19.05, dpi = 300
  #   )
  #   
```

#### Table: Route and method of administration across all responses

```{r}

  df |>
    select(-response_id) |>
  tbl_cross(
    margin = c("column", "row"), 
    percent = "cell"
  )

```

#### Figure: Route and method of administration across all responses

```{r}

  g1 <- df |>
    ggplot(aes(x = value, fill = name)) +
      geom_bar() +
      scale_fill_viridis(
        "", option = "A", begin = 0.4, discrete = TRUE
        ) +
      coord_flip() +
      ylab("Number of responses") +
      xlab("")

  g2 <- df |>
    ggplot(aes(x = value, fill = name)) +
      geom_bar(position = "fill") +
      scale_fill_viridis(
        "", option = "A", begin = 0.4, discrete = TRUE
        ) +
      coord_flip() +
      ylab("Proportion of responses") +
      xlab("") +
      theme(axis.text.y = element_blank())
  
  g1 + g2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")

```

#### Figure: Method of administration across all responses

```{r}

  df |>
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(x = value, fill = n)) +
    geom_bar() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = FALSE, begin = 0.5
      ) +
    coord_flip() +
    xlab("") +
    ylab("Responses") +
    labs(caption = "n = 347 total reponses across 45 respondents")
  
```

#### Figure: Location of administration across all responses

```{r}

  df |>
    group_by(name) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(name = reorder(factor(name), n)) |>
  ggplot(aes(x = name, fill = n)) +
    geom_bar() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = FALSE, begin = 0.5
      ) +
    coord_flip() +
    xlab("") +
    ylab("Responses")  +
    labs(caption = "n = 347 total reponses across 45 respondents")
  
```

#### Figure: Method of administration - Healthcare

```{r}

  data |>
    select(response_id, starts_with("q20_1")) |> 
    pivot_longer(-response_id) |>
    mutate(name = gsub("q20_1_", "", name)) |>
    na.omit() |> 
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(x = value, fill = value)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = TRUE, begin = 0.4
      ) +
    xlab("") +
    ylab("Number of trials")
      
```

#### Figure: Method of administration - Home

```{r}

  data |>
    select(response_id, starts_with("q20_2")) |> 
    pivot_longer(-response_id) |>
    mutate(name = gsub("q20_2_", "", name)) |>
    na.omit() |> 
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(x = value, fill = value)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = TRUE, begin = 0.4
      ) +
    xlab("") +
    ylab("Number of trials")
      
```

#### Figure: Method of administration - Community

```{r}

  data |>
    select(response_id, starts_with("q20_3")) |> 
    pivot_longer(-response_id) |>
    mutate(name = gsub("q20_3_", "", name)) |>
    na.omit() |> 
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(x = value, fill = value)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = TRUE, begin = 0.4
      ) +
    xlab("") +
    ylab("Number of trials")
      
```

#### Figure: Method of administration - Educational

```{r}

  data |>
    select(response_id, starts_with("q20_4")) |> 
    pivot_longer(-response_id) |>
    mutate(name = gsub("q20_4_", "", name)) |>
    na.omit() |> 
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(x = value, fill = value)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = TRUE, begin = 0.4
      ) +
    xlab("") +
    ylab("Number of trials")
      
```

#### Figure: Method of administration - Academic/research

```{r}

  data |>
    select(response_id, starts_with("q20_5")) |> 
    pivot_longer(-response_id) |>
    mutate(name = gsub("q20_5_", "", name)) |>
    na.omit() |> 
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(x = value, fill = value)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = TRUE, begin = 0.4
      ) +
    xlab("") +
    ylab("Number of trials")
      
```

#### Figure: Method of administration - Combination

```{r}

  data |>
    select(response_id, starts_with("q20_6")) |> 
    pivot_longer(-response_id) |>
    mutate(name = gsub("q20_6_", "", name)) |>
    na.omit() |> 
    group_by(value) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(value = reorder(factor(value), n)) |>
  ggplot(aes(x = value, fill = value)) +
    geom_bar() +
    coord_flip() +
    scale_fill_viridis(
      guide = "none", option = "A", discrete = TRUE, begin = 0.4
      ) +
    xlab("") +
    ylab("Number of trials") 
      
```

#### Free text

```{r}

  data |>
    select(starts_with("q20_7")) |> 
    remove_empty() |> 
    unlist() |>
    unique() 

```

## (Q21) Importance 

```{r}

  data |>
   select(starts_with("q21")) |> 
  tbl_summary(
    missing = "ifany",
    missing_text = "Missing or not applicable",
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) 

```

```{r}

  # To plot likert scales items, we need to first create a dataset where the
  # variables are named as their labels, and to all have a consistent set of
  # levels. This function does that by taking wide data, reshaping to long in
  # order to rename the variables and ensure the levels are the same, and then
  # reshaping back to wide.
  likert_data <- function(data, variables, var_labs, resp_levs){

      df <- data |>
        pivot_longer(
          cols = variables, names_to = "question", values_to = "response"
          ) |>
        mutate(
          question = factor(question, levels = variables, labels = var_labs), 
          response = factor(response, levels = resp_levs)
          ) |>
        pivot_wider(
          id_cols = c(pid), # ID (you might also need to add a group here)
          names_from = "question", 
          values_from = "response"
          ) 
      
    class(df) <- class(df)[3] # likert() can't handle the tibble
    return(df)
    }
  

  # To plot the data, you first need to call likert() using the data you just
  # created with the function above.
  likert_plot <- function(data, start, end, n_levs, ...){
    
    plot(likert(data[start:end]),
      col = viridis(n_levs, option = "A", begin = 0.2),
      panel.strip.color = col2, 
      wrap = 100, 
      text.color = col1 
      ) +
      guides(fill = guide_legend(
        title = "", nrow = 2, byrow = TRUE
        )) +
      ylab("") +
      theme(
        panel.grid = element_blank(), 
        legend.position = "bottom", 
        legend.key.size = unit(0.5,"line"), 
        axis.text.y = element_text(size = 7)
      ) 
    }

```

```{r}

  # Variable names
  vars <- names(select(data, starts_with("q21")))
  # Variable labels
  labs <- unlist(map(data[vars], attr, "label"))
  # Response levels
  levs <- levels(data$q21_1)

  df <- data |> 
    select(pid, all_of(vars)) |>
    likert_data(vars, labs, levs) 
  
  g1 <- likert_plot(df, 2, 39, 5) 
  
  g1
  
```

## (Q22) Other influences on use of core outcome sets 

#### Free text

```{r}

  data |>
    select(starts_with("q22")) |> 
    remove_empty() |> 
    unlist() |>
    unique() 

```

## (Q23) Other influences on choice of outcomes 

#### Free text

```{r}

  data |>
    select(starts_with("q23")) |> 
    remove_empty() |> 
    unlist() |>
    unique() 

```

## Where respondents learned about the survey (Q24)


#### Table: Where respondents learned about the survey.

```{r}

  levs <- names(select(data, starts_with("q24")))
  x <- unlist(
    str_split(meta_data$labels[meta_data$var_name %in% levs], " - ")
    )
  labs <- x[1:length(x) %% 2 == 0]

  df <- data |>
    select(response_id, starts_with("q24")) |> 
    map_df(as.character) |>
    pivot_longer(-response_id, names_to = "sources", values_to = "value") |>
    filter(value != "0") |>
    na.omit() |> 
    mutate(sources = factor(sources, levels = levs, labels = labs)) |>
    group_by(sources) |>
    mutate(n = n()) |>
    ungroup() |>
    mutate(sources = reorder(factor(sources), n))

  attr(df$sources, "label") <- "How did you hear about this survey?"
  
  df |>
    select(sources) |>
  tbl_summary(
    missing = "ifany", 
    missing_text = "Missing values",
    type = sources ~ "categorical",
    statistic =  all_categorical() ~ "{n}/{N_nonmiss} ({p}%)"
    ) 
    

```

